Spreading of a Facebook Application

### 2011-04-16 paper.tex
abstract updated

Results show that participants who connect the network of existing
users to a new one often achieved a relatively high score in the quiz. New
participants often had strong connections to the network of people who
already participated. Indeed, the number of friends did not seem to make
users more or less likely to gather new participants for the quiz.
\end{abstract}

@@

\section{Introduction}
\label{sec:introduction}
Founded in 2004, Facebook\footnote{www.facebook.com} has
become a social network currently used by more than 600 million people
all over the world\cite{facebook500}. Since 2007, Facebook provides an API permitting
third party developers to embed their own applications in
Facebook\footnote{http://developers.facebook.com/blog/archive}.
Subsequent to the F8 conference in April, 2010, Facebook simplified
access to its social graph by allowing
external websites for integration in their social graph through Open
Graph Protocol\cite{facebookStats} .

Due to integration in Facebook's social graph, third party
applications not only spare user authentication procedures, but can also access
extracts of Facebook's social graph, too. These information provided
by Facebook detail a user's friend list, basic information, and
further data to which access has to be granted by access tokens
\footnote{http://developers.facebook.com/docs/authentication/}. Thus,
applications let Facebook's social graph enlarge and make people
spend more time of Facebook. In addition, application developers
can spread their application virally through appearance in news
streams, and collect useful information about the social network of
their users, too.

Statistics show development of Facebook applications being very
attractive nowadays. Until October, 2009, 
over 350 000 apps had been seen on Facebook \cite{facebookBlog}.
According to current statistics, about 20 million applications are
installed per day, and ten thousand new websites integrate with
Facebook every day, too. \cite{facebookStats}

This paper investigates the process of spreading of applications on
Facebook by focusing on the show case of a quiz asking users five randomly
selected questions about dentistry health facts. User data are
collected in a MySQL database, and evaluation of the data is
accomplished by the outputs of a tool maintaining an internal representation of the extract of Facebook's
social graph the application is allowed to access.

The tool allows for output of graphs in \ac{dot} language and output of
metrics as \ac{csv}. The graphs the tool can output detail how the application
spreads, and allows for labelling of people (nodes) which connect the
network of existing user to new networks. The metrics detail with how
many people users who participated are friends, which score they had,
and to how many new people they could have spread the application.

In the first section, basic information about Facebook's social graph,
and integration of applications is
given. In the next section, the methodology is described by detailing
the quiz and its building, as well as the tool for data evaluation. Section
\ref{sec:results} presents the results, and in section
\ref{sec:discussion} and \ref{sec:outlook}, a discussed follows. Section
\ref{sec:conclusion} concludes the paper by summing up the results,
and giving an outlook for further research, too.

\section{Foundations}
\label{sec:background}
This section details concepts from Facebook, basics about the
\ac{DOT} language, and at least, it defines the metrics the tool
explained in section \ref{sec:methodology} can output. Facebook's
social graph concept is explained in 
section \ref{sec:social-graph}, section \ref{sec:integr-appl-with}
describes how applications can be integrated with Facebook, and
section \ref{sec:auth-auth} makes clear how applications can be
integrated with Facebook.

@@

\section{Conclusion and Outlook}
\label{sec:conclusion}
This research indicates, that their is not just one default pattern
after which applications spread on Facebook. Instead, several facts
seem to influence this effect. On the one hand, the topic of an
application and an applications type hit the interest of specific
people. Furthermore, there are often

@@

\begin{figure}
  \includegraphics[width=5in]{../img/friendsScored.png}
\caption{Figure shows all users stored in the database. Users who
  participated have a red text color.}
\label{fig:friendsScored}
\end{figure}

\begin{figure}
  \includegraphics[width=5in]{../img/friendsFilled.png}
\caption{Figure shows all users stored in the database. Users who
  participated have a red text color.}
\label{fig:friendsFilled}
\end{figure}

>>>>

Results show that participants who connect the network of existing
users to a new one often achieve a comparatively high score in the
quiz. In the most cases, new participants have strong relations to the network of people who
already participated. Indeed, the number of friends does not seem to
have any effect on whether a user gathers new participants for the quiz.
\end{abstract}

@@

\section{Introduction}
\label{sec:introduction}
Founded in 2004 Facebook\footnote{www.facebook.com} has
become a social network currently used by more than 600 million people
all over the world\cite{facebook500}. Since 2007, Facebook provides an API, permitting
third party developers to embed their own applications into
Facebook\footnote{http://developers.facebook.com/blog/archive}.
Subsequent to the F8 conference in April, 2010, Facebook simplifies
access to its social graph by allowing
external websites for integration in their social graph through Open
Graph Protocol.\cite{facebookStats}

Due to integration in Facebook's social graph, third party
applications not only spare user authentication procedures, but can also access
extracts of Facebook's social graph, too. These information detail a
user's friend list, basic information, and 
further data. Access to these data has to be granted by access tokens
\footnote{http://developers.facebook.com/docs/authentication/}. Thus,
applications let Facebook's social graph enlarge and make people
spend more time on Facebook. In addition, application developers
can spread their application virally in news
streams, and thereby they collect useful information about the social network of
their users.

Statistics show that the development of Facebook applications is becoming more
and more popular. Until October 2009, 
over three hundred fifty thousand applications have appeared on Facebook \cite{facebookBlog}.
According to current statistics about twenty million applications are
installed every day, and ten thousand new websites integrate with
Facebook every day. \cite{facebookStats}

This paper investigates the way applications spread on
Facebook. For this purpose, a quiz was built asking users five randomly
selected questions about dentistry health facts. User data are
collected in a MySQL database. The Evaluation of the data is
accomplished through the output of a tool which maintains an internal
representation of the extract of Facebook's 
social graph the application is allowed to access.

The tool allows for the output of graphs in \ac{dot} language and the output of
metrics as \ac{csv}. The graphs the tool puts out detail how the application
spreads, and allow for labelling of people (nodes) that connect the
network of existing user to new networks. The metrics detail the
number of friends users have, the average score,
and finally, the amount of users gained through the participant.

In the first section, basic information about Facebook's social graph,
and integration of applications is
given. In the next section, the methodology is described by detailing
the quiz and its implementation, as well as a tool created for data
evaluation. Section 
\ref{sec:results} presents the results, and in section
\ref{sec:discussion}, a discussion follows. Section
\ref{sec:conclusion} concludes the paper by summing up the results,
and giving an outlook on further research.

\section{Foundations}
\label{sec:background}
This section details concepts from Facebook, basics about the
\ac{dot} language, and finally, it defines the metrics the
data-evaluation tool (see section \ref{sec:methodology}) can put out. Facebook's
social graph concept is explained in 
section \ref{sec:social-graph}, section \ref{sec:integr-appl-with}
describes how applications can be integrated with Facebook, and
section \ref{sec:auth-auth} makes clear how applications can be
integrated with Facebook.

@@

\section{Conclusion and Outlook}
\label{sec:conclusion}
This research indicates that no default patterns exist describing the 
spreading of applications on Facebook. Instead, a variety of
factors seems to contribute to the investigated process. On the one
hand, the application's topic limits the target group
automatically.

Beside the 
applications topic, which limits the target group to people naturally,

seem to influence this effect: On the one hand, the chosen topic of an
application 
people. On the other hand, their are factors such as the number of

Furthermore, there

@@

% \begin{figure}
%   \includegraphics[width=5in]{../img/friendsScored.png}
% \caption{Figure shows all users stored in the database. Users who
%   participated have a red text color.}
% \label{fig:friendsScored}
% \end{figure}

% \begin{figure}
%   \includegraphics[width=5in]{../img/friendsFilled.png}
% \caption{Figure shows all users stored in the database. Users who
%   participated have a red text color.}
% \label{fig:friendsFilled}
% \end{figure}
